Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
LIPICS style

 
 \documentclass[manuscript,screen=true, review, anonymous]{acmart}

@@

 \usepackage{balance}
 \usepackage[english]{babel}
 \usepackage{blindtext}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{patterns} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}

@@

 \author{Maciej Pacut}
 \email{maciej.pacut@univie.ac.at}
 \orcid{0000-0002-6379-1490}
 \affiliation{%
 \institution{Faculty of Computer Science, University of Vienna}
 \country{Austria}
 }

 \author{Mahmoud Parham} 
 \email{mahmoud.parham@univie.ac.at}
 \orcid{0000-0002-6211-077X}
 \affiliation{%
 \institution{Faculty of Computer Science, University of Vienna}
 \country{Austria}
 }

 \author{Stefan Schmid} 
 \email{stefan_schmid@univie.ac.at}
 \affiliation{%
 \institution{Faculty of Computer Science, University of Vienna}
 \country{Austria}
 }

 \copyrightyear{2020} 
 \acmYear{2020} 
 \setcopyright{acmlicensed}
 \acmConference{DISC '20}{October 12-16, 2020}{Freiburg, Germany}

 \keywords{online algorithms, competitive analysis, graph partitioning, clustering}
 \acmISBN{}\acmPrice{}
 \acmDOI{}

@@

 \newtheorem{claim}{Claim}
 \newtheorem{fact}{Fact}
 \newtheorem{rem}{Remark}
 \newtheorem{observation}{Observation}
 \newtheorem{property}{Property}

@@

\renewcommand{\shortauthors}{M.~Pacut, M.~Parham, S.~Schmid}

@@

\maciek{TODO style: documentclass[a4paper,anonymous,USenglish] lipics-v2019.}
\maciek{Keywords: distributed computing?}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\appendix

>>>>

 \documentclass[a4paper,anonymous,USenglish]{lipics-v2019}

@@

 \usepackage{balance}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{patterns} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}

@@

 \author{Maciej Pacut}{maciej.pacut@univie.ac.at}{Faculty of Computer Science, University of Vienna,Austria}{0000-0002-6379-1490}{}

 \author{Mahmoud Parham}{mahmoud.parham@univie.ac.at}{Faculty of Computer Science, University of Vienna, Austria}{0000-0002-6211-077X}{}

 \author{Stefan Schmid}{stefan\_schmid@univie.ac.at}{Faculty of Computer Science, University of Vienna, Austria}{}{}

% \copyrightyear{2020} 
% \acmYear{2020} 
% \setcopyright{acmlicensed}
% \acmConference{DISC '20}{October 12-16, 2020}{Freiburg, Germany}

 \keywords{online algorithms, competitive analysis, distributed computing, graph partitioning, clustering, self-adjusting networks}
% \acmISBN{}\acmPrice{}
% \acmDOI{}

@@

 %\newtheorem{claim}{Claim}
 \newtheorem{fact}{Fact}
 \newtheorem{rem}{Remark}
 \newtheorem{observation}{Observation}
 \newtheorem{property}{Property}

@@

%\renewcommand{\shortauthors}{M.~Pacut, M.~Parham, S.~Schmid}

@@

@@

\bibliographystyle{plainurl}
\bibliography{references}
\appendix
